Impact of frequent assimilation of surface and satellite observations in an MCS case during RELAMPAGO field campaign. Part I: impact on the analysis

### 2021-06-25 analysis/chapters/paper_ana_20181122.Rmd
Figura del dominio aproximadamente lista.

---
title: "Impact of frequent assimilation of surface and satellite observations in an MCS case during RELAMPAGO field campaign. Part I: impact on the analysis"
author:
- name: Paola Belén Corrales
  email: paola.corrales@cima.fcen.uba.ar
  affiliation: UBA,CIMA,CNRS
  footnote: 1
- name: Victoria Galligani
  affiliation: UBA,CIMA,CNRS
- name: Juan Ruiz
  affiliation: UBA,CIMA,CNRS
- name: Luiz Sapucci
  affiliation: INPE
- name: María Eugenia Dillon
  affiliation: SMN,CONICET
- name: Yanina García Skabar
  affiliation: SMN,CONICET,CNRS
- name: Maximiliano Sacco
  affiliation: SMN
date: "`r Sys.Date()`"
output:
  rticles::elsevier_article: 
    keep_tex: true
abstract: |
  The impact of assimilating high-resolution surface networks and satellite observations using the WRF-GSI-LETKF is evaluated. We conducted a case study corresponding to a huge mesoscale convective system (MCS) developed over central and north-eastern Argentina during November, 22th, 2018. The accumulated precipitation observed during the transit of the MCS was quite high with values over 200 mm over the northern part of the domain. This MCS developed during the Intense Observing Period (IOP) of the RELAMPAGO field campaign during Nov. 2018.

@@

journal: Atmospheric Research
layout: authoryear,preprint,review,12pt
#layout: final,5p,times,twocolumn,authoryear
address:
- code: UBA
  address: Universidad de Buenos Aires, Facultad de Ciencias Exactas y Naturales, Departamento de Ciencias de la Atmósfera y los Océanos. Buenos Aires, Argentina.
- code: CIMA
  address: CONICET – Universidad de Buenos Aires. Centro de Investigaciones del Mar y la Atmósfera (CIMA). Buenos Aires, Argentina.
- code: CNRS
  address: CNRS – IRD – CONICET – UBA. Instituto Franco-Argentino para el Estudio del Clima y sus Impactos (IRL 3351 IFAECI). Buenos Aires, Argentina.
- code: SMN
  address: Servicio Meteorológico Nacional de Argentina
- code: CONICET
  address: CONICET (Consejo Nacional de Investigaciones Científicas y Técnicas)
- code: INPE
  address: National Institute for Space Research, Brazil, Center for Weather Forecasting and Climate Studies
bibliography: paper_ANA.bib
csl: elsevier-harvard.csl
footnote:
- code: 1
  text: Corresponding Author
keywords: Regional Data Assimilation, Surface Obsevations, Satellite Observations 
numbersections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	eval = FALSE,
	fig.path = "../figures/",
	fig.retina = TRUE,
	message = FALSE,
	warning = FALSE,
	collapse = TRUE,
	comment = "#>",
	dev = "png",
	dpi = 300,
	include = FALSE
)
library(mesoda)
library(metR)
library(tidyverse)
library(lubridate)
library(data.table)
library(here)
library(patchwork)
library(unglue)
library(knitr)
library(kableExtra)
library(tagger)

@@

To reduce the effect of spurious correlations in the estimation of error covariances, we use a horizontal localization radius of 180 km and a vertical localization radius of 0.4 (in log pressure coordinates) as in [RRA] for all types of observations. A relaxation-to-prior inflation [Whitaker and Hamill] is applied with an inflation parameter $\alpha=0.9$ to mitigate the impact of sampling errors and to consider model errors not accounted for by the multi-model ensemble approach.

We use a 60-member ensemble where the ensemble mean at the beginning of the data assimilation cycle is initialized using the GFS deterministic analysis. Since the publicly available GFS ensemble members change at each cycle (alguna fuente) we used random perturbations to generate the initial ensemble perturbations. This method also helps to prevent an underestimation of the ensemble spread [@ouaraini2015]. The perturbations are generated as scaled differences between two random atmospheric states obtained from the Climate Forecast System Reanalysis (CFSR) with a smooth time evolution as in [@necker2020, @maldonado2021]. In this way, we preserved the nearly hydrostatic and geostrophic equilibrium of larger scales. These random perturbations are also applied at the boundaries in order to keep the ensemble spread within the domain.

@@

```{r dominio, fig.cap="a) The horizontal domain used on the simulations (black box) and the inner domain used for the experiment comparison (red box) and the locations of Automatic Surface Weather Stations (ASWS, green squares) and Conventional Surface Weather Stations (CSWS, orange triangles) . b) Locations of radiosonde launches during the experiment, green dots corresponds to radiosondes launched during IOP07, orange triangles are radiosondes launched during IOP08 and purple square are radiosondes launched outside the IOPs. The topography in meters is also shown (filled contours).", out.width="110%"}

@@

lista_sondeos <- fread(here("analysis/data/derived_data/lista_sondeos.csv")) %>% 
  .[, periodo := fcase(nominal_launch_time %between% c(ymd_hms("20181121150000"), ymd_hms("20181121210000")),  "IOP07", 
                       nominal_launch_time %between% c(ymd_hms("20181122140000"), ymd_hms("20181122200000")),  "IOP08", 
                       default = "Others")
  ]

@@

dominio %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = hgt), proj = norargentina_lambert,
                    breaks = seq(0, 6000, 500)) +
  scale_fill_gradient(low = "#f2f2f2", high = "#333333",
                      name = NULL,
                      breaks = seq(0, 6000, 1000),
                      guide = guide_colorstrip(barwidth = 20,
                                               barheight = 0.5)) +
  geom_mapa() +
  geom_point(data = obs, aes(ConvertLongitude(lon), lat, 
                             color = source, shape = source), 
             size = 1, alpha = 0.8) + 
  scale_shape_manual(name = "a) Surface stations",  
                     breaks = c("Sfc - Non-official", "Sfc - Official"),
                     labels = c("ASWS","CSWS"), values = c(15, 17),
                     guide = guide_legend(override.aes = list(size = 2))) +
  scale_color_manual(name =  "a) Surface stations", 
                     values = c("Sfc - Non-official" = "#00695c", 
                                "Sfc - Official" = "#FD8002"),
                     breaks = c("Sfc - Non-official", "Sfc - Official"),
                     labels = c("ASWS","CSWS"),
                     guide = guide_legend(override.aes = list(size = 2))) +
  geom_point(data = square, aes(lon, lat), size = 0.2) +
  geom_point(data = square2, aes(lon, lat), size = 0.2, color = "#CC3311") +
  theme_minimal(base_size = 9) +
  theme(legend.position = "bottom", 
        legend.box = "vertical") +
  # ,
  # legend.margin = margin(),
  # legend.box.spacing = margin(0, 0, 0, 0)) +
  # 
  dominio %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = hgt), proj = norargentina_lambert,
                    breaks = seq(0, 6000, 500)) +
  scale_fill_gradient(low = "#f2f2f2", high = "#333333",
                      name = NULL,
                      breaks = seq(0, 6000, 1000),
                      guide = guide_colorstrip(barwidth = 20,
                                               barheight = 0.5)) +
  geom_mapa() +
  coord_sf(ylim = c(-35.5, -29), xlim = c(-66.5, -61.5)) +
  geom_jitter(data = lista_sondeos, aes(lon, lat, 
                                        color = periodo,
                                        shape = periodo), 
              alpha = 0.5, size = 1.5, width = 0.03, height = 0.03) +
  scale_color_brewer(palette = "Dark2",
                     guide = guide_legend(override.aes = list(size = 2,
                                                              alpha = 1))) +
  labs(color = "b) Soundings", shape = "b) Soundings") +
  theme_minimal(base_size = 9) +
  theme(legend.position = "bottom", 
        legend.box = "vertical") +
  # ,
  #         legend.margin = margin(),
  #         legend.box.spacing = margin(0, 0, 0, 0)) +
  plot_layout(ncol = 2, widths = c(4, 1), guides = "collect") +
  plot_annotation(tag_levels = 'a', tag_suffix = ')') & 
  theme(legend.position = 'bottom', legend.box = "vertical")
```

@@

```{r dist_obs, fig.cap="a) Horizontal spatial distribution of the mean available observations per analysis cycle for CONV, AUT and SATWND. b) Number of radiance observations assimilated at each analysis cycle and pressure level."}
files <- Sys.glob("/home/paola.corrales/datosmunin3/EXP/E2/ANA/*/diagfiles/asim*ensmean")[1:67]

@@

```{r count_obs, fig.cap="a) Number of available observations per cycle during the experiment. a) Vertical spatial distribution of the mean available observations per analysis cycle."}
rad2 <- rad[, .(press, iuse, error, exp, date)] %>% 
  setnames(c("press", "iuse", "error"), c("pressure", "usage.flag", "rerr"))

@@

```{r rcrv-sfc, fig.cap="Standar deviation of rcrv calculate for surface observations included in boxes of 2.5 degree"}

@@

```{r rcrv-profile, fig.cap="Profiles of the mean and standard deviation of RCRV for upper-air observations.", fig.subcap=c("Sounding and aircraft observations.", "Satellite-derived wind.", "Radiances observations.")}

@@

```{r TQ-diff, fig.cap="Difference between experiments AUT-CONV (a and b), SATWND-AUT (b and e) and RAD-SATWND (c-f) for the spatially averaged vertical profile of temperature (a, b, and c, in K) and specific humidity (d, e, and f in gkg-1).", fig.env="figure*", fig.height=3.5}
files <- list.files(derived_data, recursive = TRUE, full.names = TRUE,
                    pattern = "perfiles_ana")

@@

```{r UV-diff, fig.cap="Difference between experiments AUT-CONV (a and b), SATWND-AUT (b and e) and RAD-SATWND (c-f) for the spatially averaged vertical profile of u wind (a, b, and c, in ms-1) and v wind (d, e, and f in ms-1). In contours the u wind for AUT (a), SATWND (b) and RAD (c) and v wind for AUT (d), SATWND (e) and RAD (f).", fig.height=3.5, fig.env="figure*"}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "U") %>% 
  .[, ":="(E5_E2 = E5 - E2,
           E6_E5 = E6 - E5,
           E8_E6 = E8 - E6)] %>% 
  melt(measure.vars = c("E5_E2", "E6_E5", "E8_E6")) %>% 
  ggplot(aes(date, lev)) +
  # geom_contour(aes(z = value)) +
  geom_contour_fill(aes(z = value, fill = stat(level)), breaks = c(seq(-2, 2, 0.2), Inf)) +
  scale_fill_divergent_discretised(guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.5)) +
  geom_contour2(aes(z = value), color = "white", size = 0.1,
                    breaks = c(seq(-2, 2, 0.2), Inf)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E2 = E5, E6_E5 = E6, E8_E6 = E8)] %>%
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value),
                breaks = seq(0, 30, 3), size = 0.2, linetype = 1, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E2 = E5, E6_E5 = E6, E8_E6 = E8)] %>%
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value),
                    breaks = seq(0, 30, 3), color = "grey30", skip = 1,
                    size = 4, stroke = 0.1) +
  labs(fill = "U (m/s)",
       x = NULL,
       y = NULL) +
  scale_y_level(breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  facet_wrap(~variable, ncol = 3,
             labeller = labeller(variable = c("E5_E2" = "**AUT** - CONV",
                                              "E6_E5" = "**SATWND** - AUT",
                                              "E8_E6" = "**RAD** - SATWND"))) +
  tag_facets(position = list(x = 0.1, y = 0.96)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3), 
        strip.text = ggtext::element_markdown())

@@

```{r summary-fields, fig.cap="a) Precipitable water (shaded) and northerly wind (contours, m/s), b) Average potential temperature for the PBL and c) Maximum CAPE and ~0-6 km wind shear over 15 m/s and 30 m/s for each experiment. All fields correspond to 00 UTC Nov, 22.", fig.height=10, fig.width=9, fig.env="figure*"}

@@

```{r pp-hov, fig.cap="Hövmoller of mean hourly accumulated precipitation for each latitude band observed (left) and simulated (right, for the ensemble mean) over the inner domain."}

@@

```{r fss, fig.cap="FSS calculated over a 6-hours moving window for different thresholds and scales."}
files <- Sys.glob("/home/paola.corrales/mesoda/analysis/data/derived_data/fss_6h_ana_ens_E[2-8].csv")

@@

```{r dbz-mean, eval=FALSE, fig.cap="Observed maximum reflectivity in the column (upper row) and ensemble mean maximum reflectivity for CONV and RAD at different times (bottom two rows).", include=FALSE}
proj_radar <- "+proj=tmerc +lon_0=-61.5 +lat_0=-32 +k_0=1 +ellps=WGS84"

@@

```{r soundings, fig.cap="RMSE and Bias of temperature, dew point temperature and wind components calculated by comparing each experiment with the RELAMPAGO soundings during IOP 7 and IOP 8."}
files <- Sys.glob("/home/paola.corrales/datosmunin3/EXP/derived_data/sondeos/ANA/sondeo_E[2568]_ana*")

>>>>

---
title: "Impact of frequent assimilation of surface and satellite observations in an MCS case during RELAMPAGO field campaign. Part I: impact on the analysis"
author:
- name: Paola Belén Corrales
  email: paola.corrales@cima.fcen.uba.ar
  affiliation: UBA,CIMA,CNRS
  footnote: 1
- name: Victoria Galligani
  affiliation: UBA,CIMA,CNRS
- name: Juan Ruiz
  affiliation: UBA,CIMA,CNRS
- name: Luiz Sapucci
  affiliation: INPE
- name: María Eugenia Dillon
  affiliation: SMN,CONICET
- name: Yanina García Skabar
  affiliation: SMN,CONICET,CNRS
- name: Maximiliano Sacco
  affiliation: SMN
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_book: 
      base_format: rticles::elsevier_article
abstract: |
  The impact of assimilating high-resolution surface networks and satellite observations using the WRF-GSI-LETKF is evaluated. We conducted a case study corresponding to a huge mesoscale convective system (MCS) developed over central and north-eastern Argentina during November, 22th, 2018. The accumulated precipitation observed during the transit of the MCS was quite high with values over 200 mm over the northern part of the domain. This MCS developed during the Intense Observing Period (IOP) of the RELAMPAGO field campaign during Nov. 2018.

@@

journal: Atmospheric Research
#layout: authoryear,preprint,review,12pt
layout: final,5p,times,twocolumn,authoryear
address:
- code: UBA
  address: Universidad de Buenos Aires, Facultad de Ciencias Exactas y Naturales, Departamento de Ciencias de la Atmósfera y los Océanos. Buenos Aires, Argentina.
- code: CIMA
  address: CONICET – Universidad de Buenos Aires. Centro de Investigaciones del Mar y la Atmósfera (CIMA). Buenos Aires, Argentina.
- code: CNRS
  address: CNRS – IRD – CONICET – UBA. Instituto Franco-Argentino para el Estudio del Clima y sus Impactos (IRL 3351 IFAECI). Buenos Aires, Argentina.
- code: SMN
  address: Servicio Meteorológico Nacional de Argentina
- code: CONICET
  address: CONICET (Consejo Nacional de Investigaciones Científicas y Técnicas)
- code: INPE
  address: National Institute for Space Research, Brazil, Center for Weather Forecasting and Climate Studies
bibliography: paper_ANA.bib
csl: elsevier-harvard.csl
footnote:
- code: 1
  text: Corresponding Author
keywords: Regional Data Assimilation, Surface Obsevations, Satellite Observations 
numbersections: true
# header-includes: 
#  - \usepackage{gensymb}
#  - \usepackage{subfig}
#  - \usepackage[inline]{showlabels}
#  - \usepackage{chngcntr}
#  - \usepackage{natbib}
#  - \usepackage{lineno}
#  - \linenumbers 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.path = "../figures/",
	fig.retina = TRUE,
	message = FALSE,
	warning = FALSE,
	collapse = TRUE,
	comment = "#>",
	dev = "png",
	dpi = 300
)
library(mesoda)
library(metR)
library(tidyverse)
library(lubridate)
library(data.table)
library(here)
library(patchwork)
library(unglue)
library(knitr)
library(kableExtra)
library(tagger)
library(cowplot)

@@

To reduce the effect of spurious correlations in the estimation of error covariances, we use a horizontal localization radius of 180 km and a vertical localization radius of 0.4 (in log pressure coordinates) as in @dillonInreview for all types of observations. 
A relaxation-to-prior inflation [@whitaker2012] is applied with an inflation parameter $\alpha=0.9$ to mitigate the impact of sampling errors and to consider model errors not accounted for by the multi-model ensemble approach.

We use a 60-member ensemble where the ensemble mean at the beginning of the data assimilation cycle is initialized using the GFS deterministic analysis. Since the publicly available GFS ensemble members change at each cycle **(alguna fuente)** we used random perturbations to generate the initial ensemble perturbations. This method also helps to prevent an underestimation of the ensemble spread [@ouaraini2015]. The perturbations are generated as scaled differences between two random atmospheric states obtained from the Climate Forecast System Reanalysis (CFSR) data with 0.5° horizontal grid spacing with a smooth time evolution as in [@necker2020; @maldonado2021]. In this way, we preserved the nearly hydrostatic and geostrophic equilibrium of larger scales. These random perturbations are also applied at the boundaries in order to keep the ensemble spread within the domain.

@@

(ref:dominio) a) The horizontal domain used on the simulations (black box), the inner domain used for the experiment comparison (red box), the region shown in b) (green box) and the locations of Automatic Surface Weather Stations (ASWS, green squares) and Conventional Surface Weather Stations (CSWS, orange triangles). b) Locations of radiosonde launches during the experiment, green dots corresponds to radiosondes launched during IOP 7, orange triangles are radiosondes launched during IOP 8 and purple square are radiosondes launched outside the IOPs. The topography in meters is also shown (filled contours).

```{r dominio, fig.cap="(ref:dominio)", out.width="100%"}

@@

lista_sondeos <- fread(here("analysis/data/derived_data/lista_sondeos.csv")) %>% 
  .[, periodo := fcase(nominal_launch_time %between% c(ymd_hms("20181121150000"), ymd_hms("20181121210000")),  "IOP 7", 
                       nominal_launch_time %between% c(ymd_hms("20181122140000"), ymd_hms("20181122200000")),  "IOP 8", 
                       default = "Others")
  ]

@@

g1 <- dominio %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = hgt), proj = norargentina_lambert,
                    breaks = seq(0, 6000, 500)) +
  scale_fill_gradient(low = "#f2f2f2", high = "#333333",
                      name = NULL,
                      breaks = seq(0, 6000, 1000),
                      guide = NULL) +
  geom_mapa() +
  geom_point(data = obs, aes(ConvertLongitude(lon), lat, 
                             color = source, shape = source), 
             size = 1, alpha = 0.8) + 
  geom_rect(aes(xmin = -66.5, xmax = -61.5, ymin = -35.5, ymax = -29), 
            color = "#7CAE00", alpha = 0) +
  scale_shape_manual(name = NULL,  
                     breaks = c("Sfc - Non-official", "Sfc - Official"),
                     labels = c("ASWS","CSWS"), values = c(15, 17),
                     guide = guide_legend(override.aes = list(size = 2))) +
  scale_color_manual(name =  NULL, 
                     values = c("Sfc - Non-official" = "#00695c", 
                                "Sfc - Official" = "#FD8002"),
                     breaks = c("Sfc - Non-official", "Sfc - Official"),
                     labels = c("ASWS","CSWS"),
                     guide = guide_legend(override.aes = list(size = 2))) +
  geom_point(data = square, aes(lon, lat), size = 0.2) +
  geom_point(data = square2, aes(lon, lat), size = 0.2, color = "#CC3311") +
  theme_minimal(base_size = 10) +
  theme(legend.box = "horizontal",
        legend.position = c(0.1, 0.95),
        legend.background = element_rect(fill = "white", color = "white"))

  temp <- dominio %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = hgt), proj = norargentina_lambert,
                    breaks = seq(0, 6000, 500)) +
  scale_fill_gradient(low = "#f2f2f2", high = "#333333",
                      name = NULL,
                      breaks = seq(0, 6000, 1000),
                      guide = guide_colorstrip(barwidth = 20,
                                               barheight = 0.5)) +
  geom_mapa() +
  coord_sf(ylim = c(-35.5, -29), xlim = c(-66.5, -61.5)) +
  # geom_jitter(data = lista_sondeos, aes(lon, lat, 
  #                                       color = periodo,
  #                                       shape = periodo), 
  #             alpha = 0.5, size = 1.5, width = 0.03, height = 0.03) +
  # scale_color_brewer(palette = "Dark2",
  #                    guide = guide_legend(override.aes = list(size = 2,
  #                                                             alpha = 1))) +
  # labs(color = "b) Soundings", shape = "b) Soundings") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom")

  legend <- get_legend(temp)

  g2 <- dominio %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = hgt), proj = norargentina_lambert,
                    breaks = seq(0, 6000, 500)) +
  scale_fill_gradient(low = "#f2f2f2", high = "#333333",
                      name = NULL,
                      breaks = seq(0, 6000, 1000),
                      guide = NULL) +
  geom_mapa() +
  coord_sf(ylim = c(-35.5, -29), xlim = c(-66.5, -61.5)) +
  geom_jitter(data = lista_sondeos, aes(lon, lat, 
                                        color = periodo,
                                        shape = periodo), 
              alpha = 0.5, size = 1.5, width = 0.03, height = 0.03) +
  scale_color_brewer(palette = "Dark2",
                     guide = guide_legend(override.aes = list(size = 2,
                                                              alpha = 1))) +
  labs(color = NULL, shape = NULL) +
  theme_minimal(base_size = 10) +
  theme(legend.box = "horizontal",
        legend.position = c(0.16, 0.92),
        legend.background = element_rect(fill = "white", color = "white"))

  ggdraw(plot_grid(plot_grid(g1, g2, ncol = 2, rel_widths = c(1, 0.5), 
                             labels = c("a)", "b)"), label_size = 10), legend, 
                   ncol = 1, rel_heights = c(1, 0.05)))

@@

```{r dist_obs, eval=FALSE, fig.cap="a) Horizontal spatial distribution of the mean available observations per analysis cycle for CONV, AUT and SATWND. b) Number of radiance observations assimilated at each analysis cycle and pressure level."}
files <- Sys.glob("/home/paola.corrales/datosmunin3/EXP/E2/ANA/*/diagfiles/asim*ensmean")[1:67]

@@

```{r count_obs, eval=FALSE, fig.cap="a) Number of available observations per cycle during the experiment. a) Vertical spatial distribution of the mean available observations per analysis cycle."}
rad2 <- rad[, .(press, iuse, error, exp, date)] %>% 
  setnames(c("press", "iuse", "error"), c("pressure", "usage.flag", "rerr"))

@@

```{r rcrv-sfc, eval=FALSE, fig.cap="Standar deviation of rcrv calculate for surface observations included in boxes of 2.5 degree"}

@@

```{r rcrv-profile, eval=FALSE, fig.cap="Profiles of the mean and standard deviation of RCRV for upper-air observations.", fig.subcap=c("Sounding and aircraft observations.", "Satellite-derived wind.", "Radiances observations.")}

@@

```{r TQ-diff, eval=FALSE, fig.cap="Difference between experiments AUT-CONV (a and b), SATWND-AUT (b and e) and RAD-SATWND (c-f) for the spatially averaged vertical profile of temperature (a, b, and c, in K) and specific humidity (d, e, and f in gkg-1).", fig.env="figure*", fig.height=3.5}
files <- list.files(derived_data, recursive = TRUE, full.names = TRUE,
                    pattern = "perfiles_ana")

@@

```{r UV-diff, eval=FALSE, fig.cap="Difference between experiments AUT-CONV (a and b), SATWND-AUT (b and e) and RAD-SATWND (c-f) for the spatially averaged vertical profile of u wind (a, b, and c, in ms-1) and v wind (d, e, and f in ms-1). In contours the u wind for AUT (a), SATWND (b) and RAD (c) and v wind for AUT (d), SATWND (e) and RAD (f).", fig.height=3.5, fig.env="figure*"}
perfiles %>% 
  dcast(lev + date ~ exp, value.var = "U") %>% 
  .[, ":="(E5_E2 = E5 - E2,
           E6_E5 = E6 - E5,
           E8_E6 = E8 - E6)] %>% 
  melt(measure.vars = c("E5_E2", "E6_E5", "E8_E6")) %>% 
  ggplot(aes(date, lev)) +
  # geom_contour(aes(z = value)) +
  geom_contour_fill(aes(z = value, fill = stat(level)), breaks = c(seq(-2, 2, 0.2), Inf)) +
  scale_fill_divergent_discretised(guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.5)) +
  geom_contour2(aes(z = value), color = "white", size = 0.1,
                    breaks = c(seq(-2, 2, 0.2), Inf)) +
  geom_contour2(data = ~.x[, .(lev, date, E5_E2 = E5, E6_E5 = E6, E8_E6 = E8)] %>%
                  melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value),
                breaks = seq(0, 30, 3), size = 0.2, linetype = 1, color = "grey30") +
  geom_text_contour(data = ~.x[, .(lev, date, E5_E2 = E5, E6_E5 = E6, E8_E6 = E8)] %>%
                      melt(id.vars = c("lev", "date")) %>% unique(), aes(z = value),
                    breaks = seq(0, 30, 3), color = "grey30", skip = 1,
                    size = 4, stroke = 0.1) +
  labs(fill = "U (m/s)",
       x = NULL,
       y = NULL) +
  scale_y_level(breaks = c(1000, 850, 750, 500, 300, 200, 100)) +
  scale_date(ini = 20181121000000, break_bin = "12 hours") +
  facet_wrap(~variable, ncol = 3,
             labeller = labeller(variable = c("E5_E2" = "**AUT** - CONV",
                                              "E6_E5" = "**SATWND** - AUT",
                                              "E8_E6" = "**RAD** - SATWND"))) +
  tag_facets(position = list(x = 0.1, y = 0.96)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3), 
        strip.text = ggtext::element_markdown())

@@

```{r summary-fields, eval=FALSE, fig.cap="a) Precipitable water (shaded) and northerly wind (contours, m/s), b) Average potential temperature for the PBL and c) Maximum CAPE and ~0-6 km wind shear over 15 m/s and 30 m/s for each experiment. All fields correspond to 00 UTC Nov, 22.", fig.height=10, fig.width=9, fig.env="figure*"}

@@

```{r pp-hov, eval=FALSE, fig.cap="Hövmoller of mean hourly accumulated precipitation for each latitude band observed (left) and simulated (right, for the ensemble mean) over the inner domain."}

@@

```{r fss, eval=FALSE, fig.cap="FSS calculated over a 6-hours moving window for different thresholds and scales."}
files <- Sys.glob("/home/paola.corrales/mesoda/analysis/data/derived_data/fss_6h_ana_ens_E[2-8].csv")

@@

```{r dbz-mean, eval=FALSE, eval=FALSE, fig.cap="Observed maximum reflectivity in the column (upper row) and ensemble mean maximum reflectivity for CONV and RAD at different times (bottom two rows).", include=FALSE}
proj_radar <- "+proj=tmerc +lon_0=-61.5 +lat_0=-32 +k_0=1 +ellps=WGS84"

@@

```{r soundings, eval=FALSE, fig.cap="RMSE and Bias of temperature, dew point temperature and wind components calculated by comparing each experiment with the RELAMPAGO soundings during IOP 7 and IOP 8."}
files <- Sys.glob("/home/paola.corrales/datosmunin3/EXP/derived_data/sondeos/ANA/sondeo_E[2568]_ana*")
